We are not the 99 percent: quantifying asphericity in the distribution of Local Group satellites

### 2018-01-31 paper/paper.tex
edit

After building the normalized variables with the simulated data we
perform  a Kolmogorov-Smirnov test with the null hypothesis of belongig
to a normal distribution with mean and standard deviation computed
from the mean and standard deviation from the data itself. 
We find that the distributions for $w$, $c/a$ and $b/a$ cannot reject
the null hypothesis.

We then build a multivariate normal distribution for the two halos and
the three variables consistent with a unidimensional normal
distribution using the vector of mean values and covariance matrix.
This means that our final covariance matrix is $6\times 6$ and takes
into account the correlations internal to a single galaxy and with its
partner. 
We compute the preferred covariance matrix and the mean distribution values
with a jackknife technique. 
That is, out of the the $n$ pairs we have, we perfom $n$ different
covariance and mean value measurement using only $n-1$ pairs. 
The reported covariance and mean values correspond to the average of
all measurements, the corresponding standard deviation also help us to
estimate the uncertainty on every reported coefficient.

This compact description allows us to generate samples of size $N$
that are consistent by construction with their parent
simulation. Finally, we use the generated samples to estimate how
commoon are the deviations from sphericity that we measure in the observational
data.  We use a single-tail test in this comparison, meaning that we
always measure the fraction of points with values smaller than the
treshold value.

>>>>

After building the normalized variables with the simulated data we
perform  a Kolmogorov-Smirnov test with the null hypothesis of belonging
to a normal distribution with mean and standard deviation computed
from the mean and standard deviation from the data itself. 
We find that the distributions for the normalized $w$, $c/a$ and $b/a$
are consistent with gaussian ditributions.

Based on this result we build a multivariate normal distribution for
the joint distributions of the normalized $w$, $c/a$ and $b/a$:

\begin{equation}
p(X; \mu, \Sigma) = \frac{1}{(2\pi)^{3/2}|\Sigma|^{1/2}} \exp\left(-\frac{1}{2}(X-\mu)^{T}\Sigma^{-1}(X-\mu)\right), 
\end{equation}
% 
where $X=[w, c/a, b/a]^{T}$ is a vector variable with the normalized
quantities, $\mu$ is the vector mean and the $\Sigma$ is the
covariance matrix.

We compute the preferred covariance matrix and the mean distribution values
with a jackknife technique. 
That is, out of the the $n$ pairs we have, we perfom $n$ different
covariance and mean value measurement using only $n-1$ pairs. 
The reported covariance and mean values correspond to the average of
all measurements, the corresponding standard deviation also help us to
estimate the uncertainty on every reported coefficient.
This compact description allows us to generate samples of size $N$
that are consistent by construction with their parent simulation.

Finally, we use the generated samples to estimate how
common are the deviations from sphericity that we measure in the
observational data.  
We use a double-tailed test in this comparison, meaning that we
always measure the fraction of points with absolute values larger than the
treshold absolute observed value.
